TGI Spinal Analysis Code

### 2022-12-15 analysis/tgi-spinal_analysis.Rmd
trying to model zero and one inflated

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
# check for pacman package and install if not found
if (!require("pacman")) install.packages("pacman")
  pacman::p_load(boot, broom, broom.mixed, brms, caret, corrplot, DHARMa, 
                 gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
                 modelsummary, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
                 rsample, rstatix, simr, tibble, tidyverse, wesanderson
                 )
```

@@

# to run zero inflated regressions need to make sure no values = 100, 
# as cannot model them, so simply minus a very small fraction from those values
df_long$beta <- ifelse(df_long$VAS==100, df_long$beta-0.0001, df_long$beta <- df_long$VAS)

# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
df_long$beta <- df_long$beta/100
df_long$ID <- factor(df_long$ID)
```

Running models as pre-registered: 
# Cold
```{r coldmod}
# Try and model all with ratings
model.cold = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + procedure + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_long %>% filter(quality == 'cold'),
                      na.action = na.omit) 
mc <- summary(model.cold)
mc
```
# Warm
```{r warmmod}
# Try and model all with ratings
model.warm = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + procedure +
                                trial_n + (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_long %>% filter(quality == 'warm'),
                      na.action = na.omit) 
mw <- summary(model.warm)
mw
```

# Burn
The burning hypothesis is only for participants that experience burning TGI 
(aka are responders)
```{r burnmod}
# First, remove non-responders
df_resp <- df_long %>% 
  filter(responder == 1)
# check n
n <- count(df_resp, 'ID')
length(n$ID)
# Try and model all with ratings
model.burn = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + procedure +
                                trial_n +(1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation + (1|ID),
                      data = df_resp %>% filter(quality == 'burn'),
                      na.action = na.omit) 
mb <- summary(model.burn)
mb
```

@@

# correlate
qual_cor <- hetcor(df_corr, type = 'spearman')
cormat <- qual_cor$correlations

# significance values
p <- cor.mtest(df_corr, type ='spearman')$p

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## Loading libraries
# check for pacman package and install if not found
if (!require("pacman")) install.packages("pacman")
  pacman::p_load(boot, broom, broom.mixed, brms, caret, corrplot, DHARMa, gamlss,
                 gghalves, ggpol, ggpubr, glmmTMB, groupdata2, lme4, lmerTest, 
                 modelsummary, polycor, RColorBrewer, rcompanion, reshape2, Rmisc,
                 rsample, rstatix, simr, tibble, tidyverse, wesanderson
                 )
```

@@

# to run zero inflated regressions need to make sure no values = 100, 
# as cannot model them, so simply minus a very small fraction from those values
df_long$beta <- ifelse(df_long$VAS==100, df_long$beta-0.0001, df_long$beta <- df_long$VAS)
df_long$beta <- df_long$beta/100

# transform variables into proportions (aka divide by 100), this makes the effect size estimates more logical
df_long$VAS <- df_long$VAS/100
df_long$ID <- factor(df_long$ID)
```

Running models as pre-registered: 
# Cold
```{r coldmod}
# Try and model all with ratings
model.cold = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + trial_n +
                                (1|ID) + (1|order),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_long %>% filter(quality == 'cold'),
                      na.action = na.omit) 
mc <- summary(model.cold)
mc

model.cold1 = gamlss(VAS ~ manipulation * condition * cold_cond + procedure + trial_n +
                                random(ID),
                    nu.formula = ~ 1+manipulation,
                    tau.formula = ~ 1+manipulation,
                    family = BEINF(mu.link = 'logit', sigma.link = 'logit', nu.link = 'logit', 
                                   tau.link = 'logit'),
                    data = test %>% filter(quality == 'cold'),
                    trace = F) 
mc1 <- summary(model.cold1)
mc1
```
# Warm
```{r warmmod}
# Try and model all with ratings
model.warm = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond +
                                trial_n + (1|ID) + (1|order),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_long %>% filter(quality == 'warm'),
                      na.action = na.omit) 
mw <- summary(model.warm)
mw
```

# Burn
The burning hypothesis is only for participants that experience burning TGI 
(aka are responders)
```{r burnmod}
# First, remove non-responders
df_resp <- df_long %>% 
  filter(responder == 1)
# check n
n <- count(df_resp, 'ID')
length(n$ID)
# Try and model all with ratings
model.burn = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + 
                                trial_n + (1|ID) + (1|order),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_resp %>% filter(quality == 'burn'),
                      na.action = na.omit) 
mb <- summary(model.burn)
mb

model.burn1 = gamlss(VAS ~ manipulation * condition * cold_cond + trial_n +
                                random(ID) + random(as.factor(procedure)),
                    nu.formula = ~ 1+manipulation,
                    tau.formula = ~ 1+manipulation,
                    family = BEINF(mu.link = 'logit', sigma.link = 'logit', nu.link = 'logit', 
                                   tau.link = 'logit'),
                    data = df_resp %>% filter(quality == 'burn'),
                    trace = F) 
mc1 <- summary(model.burn1)
mc1
```

@@

# correlate
qual_cor <- hetcor(df_corr, type = 'pearson')
cormat <- qual_cor$correlations

# significance values
p <- cor.mtest(df_corr, type ='pearson')$p

@@

```{r initmod}
# Try and model all with ratings
model.init = glmmTMB::glmmTMB(beta ~ manipulation * condition * cold_cond + 
                                trial_n + (1|ID) + (1|order),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_long %>% filter(quality == 'init'),
                      na.action = na.omit) 
mi <- summary(model.init)
mi

model.burn1 = gamlss(VAS ~ manipulation * condition * cold_cond + trial_n +
                                random(ID) + random(as.factor(procedure)),
                    nu.formula = ~ 1+manipulation,
                    tau.formula = ~ 1+manipulation,
                    family = BEINF(mu.link = 'logit', sigma.link = 'logit', nu.link = 'logit', 
                                   tau.link = 'logit'),
                    data = df_resp %>% filter(quality == 'burn'),
                    trace = F) 
mc1 <- summary(model.burn1)
mc1
```
